Computer Science House Constitution

### 2024-09-22 constitution.tex
add frogperson

@@

>>>>

\asubsubsection{Responsibilities of the Frogperson}
\begin{enumerate}
	\item To act as the Shadow Board director pulling the strings of the E-Board behind the scenes.
\end{enumerate}

@@

\asubsubsection{Qualifications for Frogperson}
\begin{enumerate}
	\item The Frogperson must be selected by the prior Frogperson during a prior Frogperson's resignation.
	\item In the event the above provision can not be fulfilled, or the position would be unfilled, the Frogperson will be chosen by the Active Member(s) whose birthday is closest to September 10th, 2003.
	\item House does not select a Frogperson; the position is filled automatically.
\end{enumerate}
